Tools and Ideas for the Proceedural Generation of Shadow Sculptures.

### 2015-12-15 paper/paper.tex
Fixed a broken reference to the appendix.

The first method is partially implemented in the file `rayTracing.py' on the branch `master' in the submitted git repository. In this method the cast shadow of each sphere and cylinder is computed individually and merged. Here is some pseudo-code for rendering the shadow of a collection of spheres and cylinders illuminated by a single point light source:

@@

Appendix \ref{a} presents a derivation of the equation of the elliptical boundary of the shadow of a sphere in the most typical case.

@@

\begin{appendices}
\chapter{A} \label{a}

>>>>

The first method is partially implemented in the file `rayTracing.py' on the branch `master' in the submitted git repository \cite{gitrepo}. In this method the cast shadow of each sphere and cylinder is computed individually and merged. Here is some pseudo-code for rendering the shadow of a collection of spheres and cylinders illuminated by a single point light source:

@@

Appendix \ref{app:ellipse_derivation} presents a derivation of the equation of the elliptical boundary of the shadow of a sphere in the most typical case.

@@

\begin{appendices}
\section{A} \label{app:ellipse_derivation}
